Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-06-22 Manuscript/manuscriptPSsuppl.tex
Updates based on issue https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/99

\begin{figure*}[]
  \centering
  \includegraphics[width=18.0cm]{../Figs/figS8.png}
  \caption{\label{HGandGLYstructuresPS}
    Overlayed snapshots of the glycerol backbone and headgroup regions from different POPS simulations.
  }
\end{figure*}

>>>>

\begin{figure*}[]
  \centering
  \includegraphics[width=18.0cm]{../Figs/figS8.png}
  \caption{\label{HGandGLYstructuresPS}
    Overlayed snapshots of the headgroup (C$_\gamma$-C$_\beta$-C$_\alpha$ carbons overlayed) and
    glycerol backbone (C$_{\rm g1}$-C$_{\rm g2}$-C$_{\rm g3}$ carbons overlayed) regions from different POPS simulations.
    Note that only one of the two O$_\gamma$ atoms in the carboxylate group from PS lipids is shown.
  }
\end{figure*}
